New lower bounds for Schur and weak Schur numbers

### 2021-04-18 article/article.tex
environnement proof -> \begin{proof}[\textsc{Proof.}]
introduction + notations / definitions

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}

@@

@@

% \include{definitions_notations.tex}

@@

\qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
Schur numbers which is relatively new. Therefore, we would not be surprised if lower bounds are later improved 
using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
 are closely related to Schur and weak Schur numbers.

\par
The fourth section gives new insight on the method that was formerly used to achieve new lower bounds for weak 
Schur numbers. The assumption behind it might have removed the optimal partitions from the search space and thus 
lowered the highest value that can be reached within it. However, algorithms based on randomness such as 
Monte-Carlo algorithms may prove to be very useful if used in a search space with more potential. For instance, such 
an algorithm could be used to find better templates and improve inequalities and lower bounds for high values of \(n\). 
This could be the subject of a future work.

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{dsfont}

@@

\renewcommand{\qedsymbol}{\(\square\)}

@@

\include{definitions_notations.tex}

@@

\qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
Schur numbers which is relatively new. Therefore, we would not be surprised if lower bounds are later improved 
using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
 are closely related to Schur and weak Schur numbers. In order to find new templates, algorithms based on 
randomness such as Monte-Carlo algorithms may prove to be very useful. This could be the subject of a future work.

\par
The fourth section gives new insight on the method that was formerly used to achieve new lower bounds for weak 
Schur numbers. The assumption behind it might have removed the optimal partitions from the search space and thus 
lowered the highest value that can be reached within it. However, the methods used to explore this search space 
are efficient as the optimum was found. Thereby Monte-Carlo algorithms may prove to be very useful if used in a 
search space with more potential. Finding a weakly sum-free partition which is better than previous lower bounds 
and which is not as regular as those obtained with templates would be extremely interesting (even if it does not 
improve current lower bounds) since it could suggest a new search space which could then be explored with the 
above mentioned methods.

### 2021-04-18 article/introduction.tex
pourcents schur
introduction + notations / definitions

\par
Before Rowley's "template"-based approach for Schur and Ramsey numbers \cite{RowleyRamsey}, the 
previous generic construction for Schur numbers was given by Abbott and Hanson \cite{AbbottHanson} in 1972 
with a recursive construction. It used to give the best lower bounds for all sufficiently large numbers. No equivalent 
was known for weak Schur numbers and as a result the best known partitions for large weak Schur numbers 
did not utilize the weakly sum-free hypothesis. As for smaller numbers, the best lower bounds were obtained 
by conducting a computer search. This search for weakly sum-free partitions relied on the recursive assumption 
that a good weakly sum-free partition into \(n+1\) colors starts with a good weakly sum-free partition into \(n\) 
colors. In 2020, Rowley introduced the notion of template for Schur and Ramsey numbers which generalizes 
Abbott and Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. Rowley also 
gives two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements over previous 
lower bounds which besides do utilize the \textit{weakly} sum-free hypothesis.

@@

@@

\begin{notation}
We denote by \([\![1,p]\!]\) the set of integers \(\{1, 2, ..., p\}\).
\end{notation}

\begin{notation}
For a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We 
also denote \(m_i = \min(A_i)\).
By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do not 
make this hypothesis since we do not always consider partitions in which every subset plays a symmetric role.
\end{notation}

\begin{definition}
A partitition is sometimes referred to as a coloring. The coloring associated to a partition \(A_1, ..., A_n\) of
\([\![1, p]\!]\) is the function \(f\) such that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition 
associated to a coloring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall c \in [\![1, n]\!], A_c = f^{-1}(c)\).
\end{definition}

>>>>

\subsection{State of the art}

\qquad Before Rowley's "template"-based approach for Schur and Ramsey numbers \cite{RowleyRamsey}, the 
previous generic construction for Schur numbers was given by Abbott and Hanson \cite{AbbottHanson} in 1972 
with a recursive construction. It used to give the best lower bounds for all sufficiently large numbers. No equivalent 
was known for weak Schur numbers and as a result the best known partitions for large weak Schur numbers 
did not utilize the weakly sum-free hypothesis.

\par
As for smaller numbers, the best lower bounds were obtained by conducting a computer search. This search for 
weakly sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) 
colors starts with a good weakly sum-free partition into \(n\) colors.

\par
In 2020, Rowley introduced the notion of template for Schur and Ramsey numbers which generalizes Abbott and 
Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. Rowley also gives two 
inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements over previous lower 
bounds which besides do utilize the \textit{weakly} sum-free hypothesis.

@@

\subsection{Sutructure of this article}

@@
